Some usefull words/expressions/sentences

### 2018-07-09 phrases.Rmd
mixed results added
2 categories done

# Expressions

@@

>>>>

  heuristics [hjuə'ristiks]

```
====== 辞典翻译: heuristics ======
  n. 启发法；启发式教学法
============ 网络释义 ============
--------- heuristics ---------
  试探法
  启发
  启发式
 representativeness heuristics
  代表性启发式
  代表性启发法
---- Advanced Heuristics -----
  高级启发式
  先进的启发式辨认引擎
```

-  posit ['pɔzit]

```
======== 辞典翻译: posit =========
  n. 假设；设想
  vt. 安置；假定
============ 网络释义 ============
----------- posit ------------
  断定
  位置
  假定
------- Posit Science --------
  研究对波赛特科学
-------- posit clause --------
  断定子句
```

- circumvent

```
====== 辞典翻译: circumvent ======
  v. 包围；智取；绕行，规避
============ 网络释义 ============
--------- circumvent ---------
  避免
  欺诈
  用计谋战胜
------ Circumvent glass ------
  防御玻璃墙
----- around circumvent ------
  绕圈子
```

-  manifest ['mænifest]

```
======= 辞典翻译: manifest =======
  n. 载货单，货单；旅客名单
  vt. 证明，表明；显示
  adj. 显然的，明显的；明白的
  vi. 显示，出现
============ 网络释义 ============
---------- MANIFEST ----------
  舱单
  清单
  显示
------ Manifest Destiny ------
  昭昭天命
  昭昭天命
  天定命运
------- cargo manifest -------
  载货清单
  货物舱单
  货物清单
```

@@

## bray2015eliminating

(Eliminating bias in classify-analyze approaches for latent class analysis)

- The latent class model, which posits a mutually exclusive and exhaustive underlying set of latent classes (i.e. subgroups) inferred from multiple categorical observed variables.

- LCA has been proven to be a useful tool for identifying qualitatively different population subgroups in a variety of disciplines.

- Classify-analyze (Clogg, 1995) is a common technique used to circumvent the challenge of not having an LCA model-based solution. This technique first classifying individuals into latent classes, and then performing a subsequent analysis treating latent class membership as known (i.e., as manifest categorical variable) in a larger model of interest.

- Fundamentally, LCA is a probability-based approach that does not require assignment of individuals to latent classes; this is one of its greatest strengths....
